Processing Code

### 2023-04-07 code/processing_code/processingcode.qmd
Part 4

# Processing Section for Vaccination Data in Albany, GA

@@

 is done, now lets save the processed data

@@

# Processing for Vaccination Data for Our Control Richmond County

## Processing 1: Getting Vaccination Totals by Control Zip 31701

>>>>

# Processing Section for Target Zip Codes

@@

@@

# Processing Section for Control Zip Code

## Processing 1: Getting Vaccination Totals by Control Zip Code 30815 in the Month of September

```{r}
#I am only interested in Covid-19 Vaccination from Richmond County which contains the target zip codes of 30815, 31705 and 31707
#by using filter() I am able to create a new dataset with vaccinations from Richmond County 
Richmond_vax_Sept <- filter(Sept_17, COUNTY_NAME == "Richmond County")

#replacing negative values with 0
Richmond_vax_Sept [Richmond_vax_Sept < 0] <- 0  
```

```{r}
#Adding a column of the total vax for each census tract (for each observation)  
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>% mutate(total_vax_Sept = sum(across(ends_with("VAX")), na.rm = T))

#total vax column for all males
Richmond_vax_Sept <- Richmond_vax_Sept  %>% rowwise() %>%   
  mutate(total_male_vax = sum(across(starts_with("M") & ends_with("VAX")), na.rm = T))

#total vax column for all females
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>%   
  mutate(total_female_vax = sum(across(starts_with("F") & ends_with("VAX")), na.rm = T))

```{r}
#total vax column for Asian male residents 
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>%   
  mutate(total_masian_vax = sum(across(starts_with("MAsianNHPI") & ends_with("VAX")), na.rm = T))

#total vax column for African American male residents
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>%   
  mutate(total_mblack_vax = sum(across(starts_with("MBlack") & ends_with("VAX")), na.rm = T))

#total vax column for other race male residents
Richmond_vax_Sept<- Richmond_vax_Sept %>% rowwise() %>%   
  mutate(total_morace_vax = sum(across(starts_with("MOtherRace") & ends_with("VAX")), na.rm = T))

#total vax column for White male residents 
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>%   
  mutate(total_mwhite_vax = sum(across(starts_with("MWhite") & ends_with("VAX")), na.rm = T))

```{r}
#total vax column for Asian female residents    
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>%   
  mutate(total_fasian_vax = sum(across(starts_with("FAsianNHPI") & ends_with("VAX")), na.rm = T))

#total vax column for African American female residents
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>%   
  mutate(total_fblack_vax = sum(across(starts_with("FBlack") & ends_with("VAX")), na.rm = T))

#total vax column for other race female residents
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>%   
  mutate(total_forace_vax = sum(across(starts_with("FOtherRace") & ends_with("VAX")), na.rm = T))

#total vax column for White female residents 
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>%   
  mutate(total_fwhite_vax = sum(across(starts_with("FWhite") & ends_with("VAX")), na.rm = T))  
```

For example(see below): I get the total Asian resident vaccinations by summing male Asian residents + female Asian residents.

```{r}
#Vax total Asian Residents
Richmond_vax_Sept$total_asian_vax <- Richmond_vax_Sept$total_masian_vax + Richmond_vax_Sept$total_fasian_vax

#Vax total for African American Residents 
Richmond_vax_Sept$total_black_vax <- Richmond_vax_Sept$total_mblack_vax + Richmond_vax_Sept$total_fblack_vax

#Vax total for Other Race Residents
Richmond_vax_Sept$total_orace_vax <- Richmond_vax_Sept$total_morace_vax + Richmond_vax_Sept$total_forace_vax

#Vax total for White Residents
Richmond_vax_Sept$total_white_vax <- Richmond_vax_Sept$total_mwhite_vax + Richmond_vax_Sept$total_fwhite_vax  
```

```{r}
#summing all residents in the age range of 05-09
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>% mutate(total_05_09_vax = sum(FAsianNHPI_05_09_VAX, MAsianNHPI_05_09_VAX, UAsianNHPI_05_09_VAX,FBlack_05_09_VAX, MBlack_05_09_VAX, UBlack_05_09_VAX,FNone_05_09_VAX, MNone_05_09_VAX, UNone_05_09_VAX,FOtherRace_05_09_VAX, MOtherRace_05_09_VAX, UOtherRace_05_09_VAX,FWhite_05_09_VAX, MWhite_05_09_VAX, UWhite_05_09_VAX, na.rm = T))

#summing all residents in the age range of 10-17
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>% mutate(total_10_17_vax = sum(FAsianNHPI_10_17_VAX, MAsianNHPI_10_17_VAX, UAsianNHPI_10_17_VAX,FBlack_10_17_VAX, MBlack_10_17_VAX, UBlack_10_17_VAX,FNone_10_17_VAX, MNone_10_17_VAX, UNone_10_17_VAX,FOtherRace_10_17_VAX, MOtherRace_10_17_VAX, UOtherRace_10_17_VAX,FWhite_10_17_VAX, MWhite_10_17_VAX, UWhite_10_17_VAX, na.rm = T))

#summing all residents in the age range of 18-44
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>% mutate(total_18_44_vax = sum(FAsianNHPI_18_44_VAX, MAsianNHPI_18_44_VAX, UAsianNHPI_18_44_VAX,FBlack_18_44_VAX, MBlack_18_44_VAX, UBlack_18_44_VAX,FNone_18_44_VAX, MNone_18_44_VAX, UNone_18_44_VAX,FOtherRace_18_44_VAX, MOtherRace_18_44_VAX, UOtherRace_18_44_VAX,FWhite_18_44_VAX, MWhite_18_44_VAX, UWhite_18_44_VAX, na.rm = T))

#summing all residents in the age range of 45-64
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>% mutate(total_45_64_vax = sum(FAsianNHPI_45_64_VAX, MAsianNHPI_45_64_VAX, UAsianNHPI_45_64_VAX,FBlack_45_64_VAX, MBlack_45_64_VAX, UBlack_45_64_VAX,FNone_45_64_VAX, MNone_45_64_VAX, UNone_45_64_VAX,FOtherRace_45_64_VAX, MOtherRace_45_64_VAX, UOtherRace_45_64_VAX,FWhite_45_64_VAX, MWhite_45_64_VAX, UWhite_45_64_VAX, na.rm = T))

#summing all residents in the age range of 65+ 
Richmond_vax_Sept <- Richmond_vax_Sept %>% rowwise() %>% mutate(total_65Plus_vax = sum(FAsianNHPI_65Plus_VAX, MAsianNHPI_65Plus_VAX, UAsianNHPI_65Plus_VAX,FBlack_65Plus_VAX, MBlack_65Plus_VAX, UBlack_65Plus_VAX,FNone_65Plus_VAX, MNone_65Plus_VAX, UNone_65Plus_VAX,FOtherRace_65Plus_VAX, MOtherRace_65Plus_VAX, UOtherRace_65Plus_VAX,FWhite_65Plus_VAX, MWhite_65Plus_VAX, UWhite_65Plus_VAX, na.rm = T))

```{r}
#Extract necessary variables only  
Richmond_vax_Sept_sums <- Richmond_vax_Sept[,c(1:4,185:204)]  
```

### Filtering the data by census tract within the 30815 zip code

```{r}
#filtering data by zip: 30815  
#All of the following FIPS or census tracts correspond to the 30815 zip code
Zip_30815_Sept <-filter(Richmond_vax_Sept_sums, FIPS=="13245010904" | FIPS=="13245010907" | FIPS=="13245010908" | FIPS=="13245010713" | FIPS=="13245010714" | FIPS=="13245010711" | FIPS=="13245010708" | FIPS=="13245010707" | FIPS=="13245010709" | FIPS=="13245010710" | FIPS=="13033950101" | FIPS=="13245010905" | FIPS=="13033950200")
```
Not that the new data set `Zip_30815_Sept` only has 7 observations because the orinigal data set only had 7 of the 13 census tracts found within the zip code 30815

### Change the column names for 30815 Sept
```{r}
colnames(Zip_30815_Sept) <- c("FIPS", "GEONAME", "COUNTY_ID", "COUNTY_NAME", "total_vax_Sept_17", "total_male_vax_Sept_17", "total_female_vax_Sept_17", "total_masian_vax_Sept_17", "total_mblack_vax_Sept_17", "total_morace_vax_Sept_17", "total_mwhite_vax_Sept_17", "total_fasian_vax_Sept_17", "total_fblack_vax_Sept_17", "total_forace_vax_Sept_17", "total_fwhite_vax_Sept_17", "total_asian_vax_Sept_17","total_black_vax_Sept_17", "total_orace_vax_Sept_17", "total_white_vax_Sept_17", "total_05_09_vax_Sept_17", "total_10_17_vax_Sept_17", "total_18_44_vax_Sept_17", "total_45_64_vax_Sept_17", "total_65Plus_vax_Sept_17") 
```

### Deleting excess environment objects and saving data as processed_data_sept
```{r}
#Only need to save processed data for the three zip codes
rm(Richmond_vax_Sept,Sept_17, codebook, Richmond_vax_Sept_sums)

#saving clean data for 30815 to processed_data folder
save_data_location4 = here("data", "processed_data", "Zip_30815", "processed_data_30815_Sept.rds")

saveRDS(Zip_30815_Sept, save_data_location4)
```

## Processing 2: Getting Vaccination Totals by Target Zips 30815 for the Month of October

```{r}
#I am only interested in Covid-19 Vaccination from Richmond County which contains the target zip codes of 30815, 31705 and 31707
#by using filter() I am able to create a new dataset with vaccinations from Richmond County 
Richmond_vax_Oct <- filter(Oct_28, COUNTY_NAME == "Richmond County")

#replacing negative values with 0
Richmond_vax_Oct [Richmond_vax_Oct < 0] <- 0  
```

```{r}
#Adding a column of the total vax for each census tract (for each observation)  
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>% mutate(total_vax_Oct = sum(across(ends_with("VAX")), na.rm = T))

#total vax column for all males
Richmond_vax_Oct <- Richmond_vax_Oct  %>% rowwise() %>%   
  mutate(total_male_vax = sum(across(starts_with("M") & ends_with("VAX")), na.rm = T))

#total vax column for all females
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>%   
  mutate(total_female_vax = sum(across(starts_with("F") & ends_with("VAX")), na.rm = T))

```{r}
#total vax column for Asian male residents 
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>%   
  mutate(total_masian_vax = sum(across(starts_with("MAsianNHPI") & ends_with("VAX")), na.rm = T))

#total vax column for African American male residents
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>%   
  mutate(total_mblack_vax = sum(across(starts_with("MBlack") & ends_with("VAX")), na.rm = T))

#total vax column for other race male residents
Richmond_vax_Oct<- Richmond_vax_Oct %>% rowwise() %>%   
  mutate(total_morace_vax = sum(across(starts_with("MOtherRace") & ends_with("VAX")), na.rm = T))

#total vax column for White male residents 
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>%   
  mutate(total_mwhite_vax = sum(across(starts_with("MWhite") & ends_with("VAX")), na.rm = T))

```{r}
#total vax column for Asian female residents    
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>%   
  mutate(total_fasian_vax = sum(across(starts_with("FAsianNHPI") & ends_with("VAX")), na.rm = T))

#total vax column for African American female residents
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>%   
  mutate(total_fblack_vax = sum(across(starts_with("FBlack") & ends_with("VAX")), na.rm = T))

#total vax column for other race female residents
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>%   
  mutate(total_forace_vax = sum(across(starts_with("FOtherRace") & ends_with("VAX")), na.rm = T))

#total vax column for White female residents 
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>%   
  mutate(total_fwhite_vax = sum(across(starts_with("FWhite") & ends_with("VAX")), na.rm = T))  
```

```{r}
#Vax total Asian Residents
Richmond_vax_Oct$total_asian_vax <- Richmond_vax_Oct$total_masian_vax + Richmond_vax_Oct$total_fasian_vax

#Vax total for African American Residents 
Richmond_vax_Oct$total_black_vax <- Richmond_vax_Oct$total_mblack_vax + Richmond_vax_Oct$total_fblack_vax

#Vax total for Other Race Residents
Richmond_vax_Oct$total_orace_vax <- Richmond_vax_Oct$total_morace_vax + Richmond_vax_Oct$total_forace_vax

#Vax total for White Residents
Richmond_vax_Oct$total_white_vax <- Richmond_vax_Oct$total_mwhite_vax + Richmond_vax_Oct$total_fwhite_vax  
```

```{r}
#summing all residents in the age range of 05-09
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>% mutate(total_05_09_vax = sum(FAsianNHPI_05_09_VAX, MAsianNHPI_05_09_VAX, UAsianNHPI_05_09_VAX,FBlack_05_09_VAX, MBlack_05_09_VAX, UBlack_05_09_VAX,FNone_05_09_VAX, MNone_05_09_VAX, UNone_05_09_VAX,FOtherRace_05_09_VAX, MOtherRace_05_09_VAX, UOtherRace_05_09_VAX,FWhite_05_09_VAX, MWhite_05_09_VAX, UWhite_05_09_VAX, na.rm = T))

#summing all residents in the age range of 10-17
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>% mutate(total_10_17_vax = sum(FAsianNHPI_10_17_VAX, MAsianNHPI_10_17_VAX, UAsianNHPI_10_17_VAX,FBlack_10_17_VAX, MBlack_10_17_VAX, UBlack_10_17_VAX,FNone_10_17_VAX, MNone_10_17_VAX, UNone_10_17_VAX,FOtherRace_10_17_VAX, MOtherRace_10_17_VAX, UOtherRace_10_17_VAX,FWhite_10_17_VAX, MWhite_10_17_VAX, UWhite_10_17_VAX, na.rm = T))

#summing all residents in the age range of 18-44
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>% mutate(total_18_44_vax = sum(FAsianNHPI_18_44_VAX, MAsianNHPI_18_44_VAX, UAsianNHPI_18_44_VAX,FBlack_18_44_VAX, MBlack_18_44_VAX, UBlack_18_44_VAX,FNone_18_44_VAX, MNone_18_44_VAX, UNone_18_44_VAX,FOtherRace_18_44_VAX, MOtherRace_18_44_VAX, UOtherRace_18_44_VAX,FWhite_18_44_VAX, MWhite_18_44_VAX, UWhite_18_44_VAX, na.rm = T))

#summing all residents in the age range of 45-64
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>% mutate(total_45_64_vax = sum(FAsianNHPI_45_64_VAX, MAsianNHPI_45_64_VAX, UAsianNHPI_45_64_VAX,FBlack_45_64_VAX, MBlack_45_64_VAX, UBlack_45_64_VAX,FNone_45_64_VAX, MNone_45_64_VAX, UNone_45_64_VAX,FOtherRace_45_64_VAX, MOtherRace_45_64_VAX, UOtherRace_45_64_VAX,FWhite_45_64_VAX, MWhite_45_64_VAX, UWhite_45_64_VAX, na.rm = T))

#summing all residents in the age range of 65+ 
Richmond_vax_Oct <- Richmond_vax_Oct %>% rowwise() %>% mutate(total_65Plus_vax = sum(FAsianNHPI_65Plus_VAX, MAsianNHPI_65Plus_VAX, UAsianNHPI_65Plus_VAX,FBlack_65Plus_VAX, MBlack_65Plus_VAX, UBlack_65Plus_VAX,FNone_65Plus_VAX, MNone_65Plus_VAX, UNone_65Plus_VAX,FOtherRace_65Plus_VAX, MOtherRace_65Plus_VAX, UOtherRace_65Plus_VAX,FWhite_65Plus_VAX, MWhite_65Plus_VAX, UWhite_65Plus_VAX, na.rm = T))

```{r}
#Extract necessary variables only  
Richmond_vax_Oct_sums <- Richmond_vax_Oct[,c(1:4,185:204)]  
```

### Filtering the data by census tract within the 30815 zip code

```{r}
#filtering data by zip: 30815  
#All of the following FIPS or census tracts correspond to the 30815 zip code

Zip_30815_Oct <-filter(Richmond_vax_Oct_sums, FIPS=="13245010904" | FIPS=="13245010907" | FIPS=="13245010908" | FIPS=="13245010713" | FIPS=="13245010714" | FIPS=="13245010711" | FIPS=="13245010708" | FIPS=="13245010707" | FIPS=="13245010709" | FIPS=="13245010710" | FIPS=="13033950101" | FIPS=="13245010905" | FIPS=="13033950200")
```

### Change the column names for 30815 Oct

```{r}
colnames(Zip_30815_Oct) <- c("FIPS", "GEONAME", "COUNTY_ID", "COUNTY_NAME", "total_vax_Oct_28", "total_male_vax_Oct_28", "total_female_vax_Oct_28", "total_masian_vax_Oct_28", "total_mblack_vax_Oct_28", "total_morace_vax_Oct_28", "total_mwhite_vax_Oct_28", "total_fasian_vax_Oct_28", "total_fblack_vax_Oct_28", "total_forace_vax_Oct_28", "total_fwhite_vax_Oct_28", "total_asian_vax_Oct_28","total_black_vax_Oct_28", "total_orace_vax_Oct_28", "total_white_vax_Oct_28", "total_05_09_vax_Oct_28", "total_10_17_vax_Oct_28", "total_18_44_vax_Oct_28", "total_45_64_vax_Oct_28", "total_65Plus_vax_Oct_28") 
```

```{r}
#Only need to save processed data for the three zip codes
rm(Richmond_vax_Oct,Oct_28, codebook, Richmond_vax_Oct_sums)

#saving clean data for 30815 to processed_data folder
save_data_location4 = here("data", "processed_data","Zip_30815", "processed_data_30815_Oct.rds")

saveRDS(Zip_30815_Oct, file = save_data_location4)
```

## Processing 3: : Getting Vaccination Totals by Target Zips 30815 for the Month of November

```{r}
#I am only interested in Covid-19 Vaccination from Richmond County which contains the target zip codes of 30815, 31705 and 31707
#by using filter() I am able to create a new dataset with vaccinations from Richmond County 
Richmond_vax_Nov <- filter(Nov_24, COUNTY_NAME == "Richmond County")

#replacing negative values with 0
Richmond_vax_Nov [Richmond_vax_Nov < 0] <- 0  
```

```{r}
#Adding a column of the total vax for each census tract (for each observation)  
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>% mutate(total_vax_Nov = sum(across(ends_with("VAX")), na.rm = T))

#total vax column for all males
Richmond_vax_Nov <- Richmond_vax_Nov  %>% rowwise() %>%   
  mutate(total_male_vax = sum(across(starts_with("M") & ends_with("VAX")), na.rm = T))

#total vax column for all females
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>%   
  mutate(total_female_vax = sum(across(starts_with("F") & ends_with("VAX")), na.rm = T))

```{r}
#total vax column for Asian male residents 
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>%   
  mutate(total_masian_vax = sum(across(starts_with("MAsianNHPI") & ends_with("VAX")), na.rm = T))

#total vax column for African American male residents
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>%   
  mutate(total_mblack_vax = sum(across(starts_with("MBlack") & ends_with("VAX")), na.rm = T))

#total vax column for other race male residents
Richmond_vax_Nov<- Richmond_vax_Nov %>% rowwise() %>%   
  mutate(total_morace_vax = sum(across(starts_with("MOtherRace") & ends_with("VAX")), na.rm = T))

#total vax column for White male residents 
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>%   
  mutate(total_mwhite_vax = sum(across(starts_with("MWhite") & ends_with("VAX")), na.rm = T))

```{r}
#total vax column for Asian female residents    
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>%   
  mutate(total_fasian_vax = sum(across(starts_with("FAsianNHPI") & ends_with("VAX")), na.rm = T))

#total vax column for African American female residents
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>%   
  mutate(total_fblack_vax = sum(across(starts_with("FBlack") & ends_with("VAX")), na.rm = T))

#total vax column for other race female residents
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>%   
  mutate(total_forace_vax = sum(across(starts_with("FOtherRace") & ends_with("VAX")), na.rm = T))

#total vax column for White female residents 
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>%   
  mutate(total_fwhite_vax = sum(across(starts_with("FWhite") & ends_with("VAX")), na.rm = T))  
```

```{r}
#Vax total Asian Residents
Richmond_vax_Nov$total_asian_vax <- Richmond_vax_Nov$total_masian_vax + Richmond_vax_Nov$total_fasian_vax

#Vax total for African American Residents 
Richmond_vax_Nov$total_black_vax <- Richmond_vax_Nov$total_mblack_vax + Richmond_vax_Nov$total_fblack_vax

#Vax total for Other Race Residents
Richmond_vax_Nov$total_orace_vax <- Richmond_vax_Nov$total_morace_vax + Richmond_vax_Nov$total_forace_vax

#Vax total for White Residents
Richmond_vax_Nov$total_white_vax <- Richmond_vax_Nov$total_mwhite_vax + Richmond_vax_Nov$total_fwhite_vax  
```

```{r}
#summing all residents in the age range of 05-09
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>% mutate(total_05_09_vax = sum(FAsianNHPI_05_09_VAX, MAsianNHPI_05_09_VAX, UAsianNHPI_05_09_VAX,FBlack_05_09_VAX, MBlack_05_09_VAX, UBlack_05_09_VAX,FNone_05_09_VAX, MNone_05_09_VAX, UNone_05_09_VAX,FOtherRace_05_09_VAX, MOtherRace_05_09_VAX, UOtherRace_05_09_VAX,FWhite_05_09_VAX, MWhite_05_09_VAX, UWhite_05_09_VAX, na.rm = T))

#summing all residents in the age range of 10-17
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>% mutate(total_10_17_vax = sum(FAsianNHPI_10_17_VAX, MAsianNHPI_10_17_VAX, UAsianNHPI_10_17_VAX,FBlack_10_17_VAX, MBlack_10_17_VAX, UBlack_10_17_VAX,FNone_10_17_VAX, MNone_10_17_VAX, UNone_10_17_VAX,FOtherRace_10_17_VAX, MOtherRace_10_17_VAX, UOtherRace_10_17_VAX,FWhite_10_17_VAX, MWhite_10_17_VAX, UWhite_10_17_VAX, na.rm = T))

#summing all residents in the age range of 18-44
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>% mutate(total_18_44_vax = sum(FAsianNHPI_18_44_VAX, MAsianNHPI_18_44_VAX, UAsianNHPI_18_44_VAX,FBlack_18_44_VAX, MBlack_18_44_VAX, UBlack_18_44_VAX,FNone_18_44_VAX, MNone_18_44_VAX, UNone_18_44_VAX,FOtherRace_18_44_VAX, MOtherRace_18_44_VAX, UOtherRace_18_44_VAX,FWhite_18_44_VAX, MWhite_18_44_VAX, UWhite_18_44_VAX, na.rm = T))

#summing all residents in the age range of 45-64
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>% mutate(total_45_64_vax = sum(FAsianNHPI_45_64_VAX, MAsianNHPI_45_64_VAX, UAsianNHPI_45_64_VAX,FBlack_45_64_VAX, MBlack_45_64_VAX, UBlack_45_64_VAX,FNone_45_64_VAX, MNone_45_64_VAX, UNone_45_64_VAX,FOtherRace_45_64_VAX, MOtherRace_45_64_VAX, UOtherRace_45_64_VAX,FWhite_45_64_VAX, MWhite_45_64_VAX, UWhite_45_64_VAX, na.rm = T))

#summing all residents in the age range of 65+ 
Richmond_vax_Nov <- Richmond_vax_Nov %>% rowwise() %>% mutate(total_65Plus_vax = sum(FAsianNHPI_65Plus_VAX, MAsianNHPI_65Plus_VAX, UAsianNHPI_65Plus_VAX,FBlack_65Plus_VAX, MBlack_65Plus_VAX, UBlack_65Plus_VAX,FNone_65Plus_VAX, MNone_65Plus_VAX, UNone_65Plus_VAX,FOtherRace_65Plus_VAX, MOtherRace_65Plus_VAX, UOtherRace_65Plus_VAX,FWhite_65Plus_VAX, MWhite_65Plus_VAX, UWhite_65Plus_VAX, na.rm = T))

```{r}
#Extract necessary variables only  
Richmond_vax_Nov_sums <- Richmond_vax_Nov[,c(1:4,185:204)]  
```

### Filtering the data by census tract within the 30815 zip code

```{r}
#filtering data by zip: 30815  
#All of the following FIPS or census tracts correspond to the 30815 zip code

Zip_30815_Nov <-filter(Richmond_vax_Nov_sums, FIPS=="13245010904" | FIPS=="13245010907" | FIPS=="13245010908" | FIPS=="13245010713" | FIPS=="13245010714" | FIPS=="13245010711" | FIPS=="13245010708" | FIPS=="13245010707" | FIPS=="13245010709" | FIPS=="13245010710" | FIPS=="13033950101" | FIPS=="13245010905" | FIPS=="13033950200")

### Change the column names for 30815 Nov

```{r}
colnames(Zip_30815_Nov) <- c("FIPS", "GEONAME", "COUNTY_ID", "COUNTY_NAME", "total_vax_Nov_24", "total_male_vax_Nov_24", "total_female_vax_Nov_24", "total_masian_vax_Nov_24", "total_mblack_vax_Nov_24", "total_morace_vax_Nov_24", "total_mwhite_vax_Nov_24", "total_fasian_vax_Nov_24", "total_fblack_vax_Nov_24", "total_forace_vax_Nov_24", "total_fwhite_vax_Nov_24", "total_asian_vax_Nov_24","total_black_vax_Nov_24", "total_orace_vax_Nov_24", "total_white_vax_Nov_24", "total_05_09_vax_Nov_24", "total_10_17_vax_Nov_24", "total_18_44_vax_Nov_24", "total_45_64_vax_Nov_24", "total_65Plus_vax_Nov_24") 
```

```{r}
#Only need to save processed data for the three zip codes
rm(Richmond_vax_Nov,Nov_24, codebook, Richmond_vax_Nov_sums)

#saving clean data for 30815 to processed_data folder
save_data_location4 = here("data", "processed_data","Zip_30815", "processed_data_30815_Nov.rds")

saveRDS(Zip_30815_Nov, file = save_data_location4)

## Processing 4: Getting Vaccination Totals by Target Zips 30815 for the Month of December

```{r}
#I am only interested in Covid-19 Vaccination from Richmond County which contains the target zip codes of 30815, 31705 and 31707
#by using filter() I am able to create a new dataset with vaccinations from Richmond County 
Richmond_vax_Dec <- filter(Dec_29, COUNTY_NAME == "Richmond County")

#replacing negative values with 0
Richmond_vax_Dec [Richmond_vax_Dec < 0] <- 0  
```

```{r}
#Adding a column of the total vax for each census tract (for each observation)  
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>% mutate(total_vax_Dec = sum(across(ends_with("VAX")), na.rm = T))

#total vax column for all males
Richmond_vax_Dec <- Richmond_vax_Dec  %>% rowwise() %>%   
  mutate(total_male_vax = sum(across(starts_with("M") & ends_with("VAX")), na.rm = T))

#total vax column for all females
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>%   
  mutate(total_female_vax = sum(across(starts_with("F") & ends_with("VAX")), na.rm = T))

```{r}
#total vax column for Asian male residents 
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>%   
  mutate(total_masian_vax = sum(across(starts_with("MAsianNHPI") & ends_with("VAX")), na.rm = T))

#total vax column for African American male residents
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>%   
  mutate(total_mblack_vax = sum(across(starts_with("MBlack") & ends_with("VAX")), na.rm = T))

#total vax column for other race male residents
Richmond_vax_Dec<- Richmond_vax_Dec %>% rowwise() %>%   
  mutate(total_morace_vax = sum(across(starts_with("MOtherRace") & ends_with("VAX")), na.rm = T))

#total vax column for White male residents 
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>%   
  mutate(total_mwhite_vax = sum(across(starts_with("MWhite") & ends_with("VAX")), na.rm = T))

```{r}
#total vax column for Asian female residents    
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>%   
  mutate(total_fasian_vax = sum(across(starts_with("FAsianNHPI") & ends_with("VAX")), na.rm = T))

#total vax column for African American female residents
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>%   
  mutate(total_fblack_vax = sum(across(starts_with("FBlack") & ends_with("VAX")), na.rm = T))

#total vax column for other race female residents
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>%   
  mutate(total_forace_vax = sum(across(starts_with("FOtherRace") & ends_with("VAX")), na.rm = T))

#total vax column for White female residents 
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>%   
  mutate(total_fwhite_vax = sum(across(starts_with("FWhite") & ends_with("VAX")), na.rm = T))  
```

```{r}
#Vax total Asian Residents
Richmond_vax_Dec$total_asian_vax <- Richmond_vax_Dec$total_masian_vax + Richmond_vax_Dec$total_fasian_vax

#Vax total for African American Residents 
Richmond_vax_Dec$total_black_vax <- Richmond_vax_Dec$total_mblack_vax + Richmond_vax_Dec$total_fblack_vax

#Vax total for Other Race Residents
Richmond_vax_Dec$total_orace_vax <- Richmond_vax_Dec$total_morace_vax + Richmond_vax_Dec$total_forace_vax

#Vax total for White Residents
Richmond_vax_Dec$total_white_vax <- Richmond_vax_Dec$total_mwhite_vax + Richmond_vax_Dec$total_fwhite_vax  
```

```{r}
#summing all residents in the age range of 05-09
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>% mutate(total_05_09_vax = sum(FAsianNHPI_05_09_VAX, MAsianNHPI_05_09_VAX, UAsianNHPI_05_09_VAX,FBlack_05_09_VAX, MBlack_05_09_VAX, UBlack_05_09_VAX,FNone_05_09_VAX, MNone_05_09_VAX, UNone_05_09_VAX,FOtherRace_05_09_VAX, MOtherRace_05_09_VAX, UOtherRace_05_09_VAX,FWhite_05_09_VAX, MWhite_05_09_VAX, UWhite_05_09_VAX, na.rm = T))

#summing all residents in the age range of 10-17
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>% mutate(total_10_17_vax = sum(FAsianNHPI_10_17_VAX, MAsianNHPI_10_17_VAX, UAsianNHPI_10_17_VAX,FBlack_10_17_VAX, MBlack_10_17_VAX, UBlack_10_17_VAX,FNone_10_17_VAX, MNone_10_17_VAX, UNone_10_17_VAX,FOtherRace_10_17_VAX, MOtherRace_10_17_VAX, UOtherRace_10_17_VAX,FWhite_10_17_VAX, MWhite_10_17_VAX, UWhite_10_17_VAX, na.rm = T))

#summing all residents in the age range of 18-44
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>% mutate(total_18_44_vax = sum(FAsianNHPI_18_44_VAX, MAsianNHPI_18_44_VAX, UAsianNHPI_18_44_VAX,FBlack_18_44_VAX, MBlack_18_44_VAX, UBlack_18_44_VAX,FNone_18_44_VAX, MNone_18_44_VAX, UNone_18_44_VAX,FOtherRace_18_44_VAX, MOtherRace_18_44_VAX, UOtherRace_18_44_VAX,FWhite_18_44_VAX, MWhite_18_44_VAX, UWhite_18_44_VAX, na.rm = T))

#summing all residents in the age range of 45-64
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>% mutate(total_45_64_vax = sum(FAsianNHPI_45_64_VAX, MAsianNHPI_45_64_VAX, UAsianNHPI_45_64_VAX,FBlack_45_64_VAX, MBlack_45_64_VAX, UBlack_45_64_VAX,FNone_45_64_VAX, MNone_45_64_VAX, UNone_45_64_VAX,FOtherRace_45_64_VAX, MOtherRace_45_64_VAX, UOtherRace_45_64_VAX,FWhite_45_64_VAX, MWhite_45_64_VAX, UWhite_45_64_VAX, na.rm = T))

#summing all residents in the age range of 65+ 
Richmond_vax_Dec <- Richmond_vax_Dec %>% rowwise() %>% mutate(total_65Plus_vax = sum(FAsianNHPI_65Plus_VAX, MAsianNHPI_65Plus_VAX, UAsianNHPI_65Plus_VAX,FBlack_65Plus_VAX, MBlack_65Plus_VAX, UBlack_65Plus_VAX,FNone_65Plus_VAX, MNone_65Plus_VAX, UNone_65Plus_VAX,FOtherRace_65Plus_VAX, MOtherRace_65Plus_VAX, UOtherRace_65Plus_VAX,FWhite_65Plus_VAX, MWhite_65Plus_VAX, UWhite_65Plus_VAX, na.rm = T))

```{r}
#Extract necessary variables only  
Richmond_vax_Dec_sums <- Richmond_vax_Dec[,c(1:4,185:204)]  
```

### Filtering the data by census tract within the 30815 zip code
